\section{Anhang}
\subsection*{Installationsanleitung}
\subsubsection*{Installation des JHelioviewers}


\subsubsection*{Installation der Kompression}
\pagebreak

\subsection*{File Format and Decompression}
This section describes the decoding and decompression algorithm used for compressing fieldline data. The data is written in the FITS Format \cite{website:fits} and compressed with Rar. The content of the FITS file is described in Table \ref{anhang:format:content}.\\
\begin{table}[!htbp]
\center
\begin{tabular}{|c|c|c|c|}
	\hline
	Name  & Datatype & Encoding& Content Description	\\\hline
    B0 & Double & None & Latitude to Earth\\
    L0 & Double& None& Longitude to Earth\\
    LINE\_LENGTH &Byte Array & Adaptive Precision U. & Length of each line\\
    START\_R & Byte Array & Adaptive Precision & Radius of start point for each line\\
    END\_R & Byte Array & Adaptive Precision & Radius of end point for each line\\
    START\_PHI & Byte Array & Adaptive Precision & Latitude of start point for each line\\
    END\_PHI & Byte Array & Adaptive Precision & Latitude of end point for each line\\
    START\_THETA & Byte Array & Adaptive Precision & Longitude of start point for each line\\
    END\_THETA & Byte Array & Adaptive Precision & Longitude of end point for each line\\
    CHANNEL\_R & Byte Array & Adaptive Precision & Radius Channel of prediction errors of each line\\
    CHANNEL\_PHI & Byte Array & Adaptive Precision & Latitude Channel of prediction errors of each line\\
    CHANNEL\_THETA & Byte Array & Adaptive Precision & Longitude Channel of prediction errors of each line\\\hline
\end{tabular}
\caption{Content of the FITS File}
\label{anhang:format:content}
\end{table}
The following steps have to be taken to decompress the fieldline data:
\begin{enumerate}
	\item Decode RAR
	\item Split the fieldlines. Each line has 1 Length, 1 start point, 1 end point and the size of ''Length'' of prediction errors.
	\item Do the Byte Decoding specified under section \ref{anhang:format:encodings}
	\item reverse the predictive coding described under section \ref{anhang:format:prediction}
	\item convert from spherical coordinate system to cartesian. Section \ref{anhang:format:euler} describes the process.
\end{enumerate}

\subsubsection*{Encodings} \label{anhang:format:encodings}
\textbf{Unsigned Adaptive Precision Encoding}\\
\begin{table}[!htbp]
	\center
	\begin{tabular}{|c|c|c|c||c|c|c|c|}
	\hline
	\multicolumn{8}{|c|}{Byte}\\\hline
	Continue Flag & X & X & X & X & X & X & X \\\hline
	\end{tabular}
	\caption{Unsigned Adaptive Byte Encoding. X are data bits.}
	\label{anhang:format:encodings:adaptiveUnsigned}
\end{table}
The Data is stored using the byte encoding in table \ref{anhang:format:encodings:adaptiveUnsigned}.If the Continue Flag is set, then the next Byte also belongs to the value. The Bytes are Stored in Big-Endian\cite{wiki:endianess} convention. The next Byte contains the 7 lesser bits if the Continue Flag is set.

\textbf{Adaptive Precision Encoding}\\
\begin{table}[!htbp]
	\center
	\begin{tabular}{|c|c|c|c||c|c|c|c|}
	\hline
	\multicolumn{8}{|c|}{Byte}\\\hline
	Continue Flag & Sign Flag & X & X & X & X & X & X \\\hline
	\end{tabular}
	\caption{Signed Adaptive Byte Encoding of the First Byte.  X are data bits.}
	\label{anhang:format:encodings:adaptive}
\end{table}
Same Principle as the Unsigned Adaptive Precision Encoding, but the First Byte of each value contains a Sign Flag as demonstrated in table \ref{anhang:format:encodings:adaptive}. Here is an example implementation:\\
\lstinputlisting[language=Java]{./source/byteDecoding.txt}

\subsubsection*{Transformation to cartesian Coordinates} \label{anhang:format:euler}
The spherical coordinates can be transformed into the sun's cartesian coordinate system with a few simple calculations.
Step 1: Add the displacement of the Compression. 
\begin{equation}
\begin{split}
	R_{raw} &= R_{raw} + 8192\\
	Phi_{raw} &= Phi_{raw} + 16384\\
	Theta_{raw} &= Theta_{raw} + 8192
\end{split}
\end{equation}
Step 2: Convert to Floating point numbers.
\begin{equation}
\begin{split}
	R &= R_{raw} / 8192 * Sunradius (Meter)\\
	Phi &= Phi_{raw} / 32768.0 * 2 *\pi\\
	Theta &= Theta_{raw} /32768.0 * 2 *\pi
	\end{split}
\end{equation}
Step 3: Rotate the coordinates so they are centered around the viewpoint of Earth.
\begin{equation}
\begin{split}
	Phi &= Phi - l0 /180 * \pi\\
	Theta &= Theta + b0 /180 * \pi
	\end{split}
\end{equation}
Step 4: Transform from spherical to cartesian.
\begin{equation}
\begin{split}
	X &= R * sinus(Theta) * sinus(Phi)\\
	Y &= R * cosinus(Theta)\\
	Z &= R * sinus(Theta) * cosinus(Phi)
	\end{split}
\end{equation}

\subsubsection*{Decode Prediction}\label{anhang:format:prediction}
Step 1, multiply the prediction errors with:
\begin{equation}
\begin{split}
	\mbox{ factor }6 & \mbox{ if index } < 5\\
	\mbox{ factor }8 & \mbox{ if } 5 \leq \mbox{ index } < 16\\
	\mbox{ factor }16 & \mbox{ if } 5 \leq \mbox{ index }
\end{split}
\end{equation}

Step 2, Decode Prediction. Here is an example implementation in Java:
\lstinputlisting[language=Java]{./source/prediction.txt}
\pagebreak

\subsection*{Performance Tests} \label{anhang:performance}
\begin{table}[!htbp]
\center
\begin{tabular}{c|c}
	Lösunsansatz & Durchschnittliche Dekompressionszeit (ms) \\\hline
	Adaptives Subsampling & $19$ ms \\
	DCT - Naive Inverse DCT & $3100$ ms \\
	DCT - Mit Kosinus Caching & $65-350$ ms\\
	DCT- Mit JTransform Kosinus Caching & $100-135$ ms\\
	Prediktive Kodierung & $31$ ms\\
\end{tabular}
\end{table}

\textbf{Testmaschine}
\begin{table}[!htbp]
\center
\begin{tabular}{c|c}
	Prozessor & Intel i7-4600 \\\hline
	Arbeitsspeicher & 16GB \\
	OS & Windows 8.1 Enterprise 64bit \\
\end{tabular}
\end{table}
